My title

### 2024-11-03 paper/paper.qmd
Update abstract

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####
library(tidyverse)
library(knitr)
library(dplyr)
library(arrow)
library(patchwork)
library(car)
library(kableExtra)
library(gridExtra)
library(moments)
library(grid)
set.seed(912)
#### Read data ####
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
test_Trump <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
test_Harris <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
full_Trump <- read_parquet(here::here("data/02-analysis_data/00-full/full_Trump.parquet"))
full_Harris <- read_parquet(here::here("data/02-analysis_data/00-full/full_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))
Harris_model <- readRDS(here::here("models/Harris_model.rds"))
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "This study aggregates polling data to forecast support for 2024 U.S. presidential candidates Kamala Harris and Donald Trump. By applying linear models with adjustments, we identify a modest lead for Harris at 47.6% over Trump’s 43.5%. The findings highlight that carefully weighted polling data provides a clearer view of electoral dynamics, showing how rigorous methodology in forecasting can yield more accurate insights into public opinion trends, aiding informed decision-making in political and economic spheres."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####
library(tidyverse)
library(knitr)
library(dplyr)
library(arrow)
library(patchwork)
library(car)
library(kableExtra)
library(gridExtra)
library(moments)
library(grid)
set.seed(912)
#### Read data ####
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
test_Trump <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
test_Harris <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
full_Trump <- read_parquet(here::here("data/02-analysis_data/00-full/full_Trump.parquet"))
full_Harris <- read_parquet(here::here("data/02-analysis_data/00-full/full_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))
Harris_model <- readRDS(here::here("models/Harris_model.rds"))
```
